---
title: IE 522 HW02
date: 9/5/2020
author: Yue Ma
output: pdf_document
---

Install the ISLR library in R. Smarket is a data frame from this library that contains returns of S\&P 500 in the five year period from 1/10/2001 to 12/30/2005. The following shows the first and last three rows of the data frame:
```{r}
library(ISLR)
n=nrow(Smarket)
Smarket[c(1:3,(n-2):n),]
```
For each date, *Today* is the percentage return of the day. *Direction* indicates whether S\&P 500 was going up or down during the day. *Volume* is the trading volume on the previous day (in billions). *Lag1* to *Lag5* are the percentage returns in the previous 5 days. From compass2g, download ISLRSmarketDates.csv and put it in your R working directory. It contains the corresponding dates. Replace the first column of Smarket by these dates.
```{r}
setwd("/home/mavy731/Documents/IE522/HW2")
dates=read.csv("ISLRSmarketDates.csv",header=TRUE)
sp=data.frame(dates,Smarket[,-1])
n=nrow(sp)
sp[c(1:3,(n-2):n),]
```


1. (1 point) Construct a histogram for *Today*. Make the vertical axis density instead of frequency. Set the number of bins to 50. \

```{r}
hist(sp$Today,breaks=50,col='azure4',prob=TRUE)
```

2. (1 point) Add a normal fit to the histogram you obtain in #1. Is the normal distribution fitting the peak well?\

  The normal distribution can approximately fit the shape of the histogram, but does not fit the peak well.\

```{r}
hist(sp$Today,breaks=50,col='azure4',prob=TRUE)
TdMean=mean(sp$Today, na.rm=TRUE)
TdStd=sd(sp$Today, na.rm=TRUE)
curve(dnorm(x,TdMean,TdStd),add=TRUE,col="chocolate3",lwd=4)
```

3. (1 point) Use the dlaplace(x,$\mu$,$b$) function in the VGAM library (dlaplace(x,$\mu$,$b$) is the pdf of a Laplace distribution with location parameter $\mu$ and scale parameter $b$), add a Laplace fit to the histogram you obtain in #1. Is the Laplace distribution fitting the peak better than normal?\

  Yes, from the diagram, the Laplace distribution fits the peak better.\

```{r}
library(VGAM)
hist(sp$Today,breaks=50,col='azure4',prob=TRUE)
TdMean=mean(sp$Today, na.rm=TRUE)
TdStd=sd(sp$Today, na.rm=TRUE)
curve(dnorm(x,TdMean,TdStd),add=TRUE,col="chocolate3",lwd=3)
curve(dlaplace(x,TdMean,TdStd),add=TRUE,col='cyan',lwd=3)
```


4. (1 point) Add KDEs to the histogram you obtain in #1 using 1/4 of the default bandwidth and four times the default bandwidth. Which fits the data better? Which is less oscillating and smoother?\

  The KDE with bandwidth adjusted by 0.25 fits the histogram better, while the KDE with bandwidth adjusted by 4 is smoother and less oscillating.\

```{r}
hist(sp$Today,breaks=50,col='azure4',prob=TRUE)
lines(density(sp$Today,bw="nrd0",adjust=0.25,na.rm=TRUE),col="blueviolet",lwd=3)
lines(density(sp$Today,bw="nrd0",adjust=4,na.rm=TRUE),col="brown2",lwd=3)
```

5. (1 point) Construct a boxplot for *Today*. Investigate the most negative outlier. What caused this extreme negative return?\

  From the boxplot, the outliers can be seen as legitimate for their continuity.\
  Following the worst terrorist attack in U.S history on Sep.11, NYSE has been shut down for one week and was re-open on 9/17/2001. The extreme drop of the S&P500 showed the market shock toward that tragic event.\

```{r}
set.seed(2)
boxplot(sp$Today,ylab='Percentage Return')
```

```{r}
outliers=boxplot(sp$Today,plot=FALSE)$out
sp[sp$Today %in% min(outliers),]
```

6. (1 point) Report the correlation matrix for all the variables excluding Date and Direction. Do you see any strong linear relationship?\

  No strong linear relationship found.\

```{r}
 round(cor(sp[,2:8],use="complete.obs"),digits=2)
```

7. (1 point) Construct a scatterplot matrix for all variables excluding Date and Direction. Do you see any significant linear or nonlinear relationship?\

  No significant linear or nonlinear relationship found.\

```{r}
pairs(sp[,2:8])
```

8. (1 point) Construct a time series plot for Volume. What do you observe near the end of each year?\

  By the end of each year, the trading volume of the market usually will have a big drop.\

```{r}
 library(xts)
 library(zoo)
d<-as.Date(sp$Date,"%m/%d/%Y")
sp_ts <-xts(sp[2:8],order.by=d)

plot(sp_ts$Volume)

```

9. (1 point) Construct a normal plot and a Laplace plot for *Today*, side by side. Make sure that the ranges of the x-axis are the same for both plots. Between the normal distribution and the Laplace distribution, which is fitting the data better?\

  From the two plots, the Laplace distribution fits the data better for being more close to a straight line.\

```{r}

normaldata<-rnorm(1000,mean=TdMean,sd=TdStd)
par(mfrow=c(1,2))

qqnorm(sp$Today,ylab="Sample Quantiles of Today",xlim=c(-6,6))
qqline(sp$Today)
qqplot(rlaplace(1000),sp$Today,xlim=c(-6,6))
qqline(sp$Today)


```

10. (1 point) Given a random sample $\{X_1,\cdots,X_n\}$ from a Laplace distribution with location parameter $\mu$ and scale parameter $b$, using the method of moments, find the point estimator for $\mu$. Show that the corresponding point estimator for b is
$$
  \hat{b}=\frac{1}{\sqrt{2}}\sqrt{\frac{1}{n}\sum_{i=1}^n(X_i-\bar{X}_n)^2}.
$$

Point estimator for $\mu$:
Let
$$\lambda=X-\mu $$
$$
  \exp(X)=\exp(\lambda+\mu)=\exp(\lambda)+\mu
$$
$$
  =\frac{1}{2b}\int_{-\infty}^0 \lambda\exp(\frac{-\lambda}{b})d\lambda+\frac{1}{2b}\int_{0}^\infty \lambda\exp(\frac{\lambda}{b})d\lambda+\mu=\mu
  $$
  $$
  \exp(X)=\frac{1}{n}\sum\limits_{i=1}^nX_i=\bar{X}_n
  $$
  $$
  \hat{\mu}=\bar{X}_n
$$


$$
\exp(X^2)=\exp((\lambda+\mu)^2)
=exp(\lambda^2+2\mu\lambda+\lambda^2)
=\exp(\lambda^2)+\mu^2
$$
$$
=\frac{1}{2b}\int_{-\infty}^0 \lambda^2 \exp(\frac{-\lambda}{b}) d\lambda+\frac{1}{2b}\int_{0}^\infty \lambda^2 \exp(\frac{\lambda}{b}) d\lambda+\mu^2
$$
$$
=2b^2+\mu^2
$$
$$
Var(X)=\exp(X^2)-(\exp(X))^2=2b^2
$$
$$
\hat{b}=\frac{1}{\sqrt{2}}\sqrt{\frac{1}{n}\sum_{i=1}^n(X_i-\bar{X}_n)^2}
$$

